FinalManuscript_DISCS_UG

### 2018-06-23 parts/01_introduction_01contextofstudy.tex
test commit

\section{Context of Study}

This subsection of the Introduction aims to discuss the fields related to your study. It is meant to benefit your readers, especially for those who have little or no background on the kind of work your study seeks to explore. You may also briefly discuss related work to help situate your reader.
A sample context can be as follows: “The use of agents within ITSs has been the subject of continuing research at the Ateneo de Manila University.  A continuum of research work has been invested particularly in the design and development of emotionally intelligent agents for Aplusix.  Early work in the area developed models of student emotion [2], [7] as well as preliminary designs for an agent [8]. The first three studies were synthesized into a working ECA [1], with an initial capability of detecting and responding to learner affect through the learner’s interaction with Aplusix. (p.2)”

>>>>

\section{Context of the Study}

Data privacy and security is a growing concern in various fields \textbf{[insert fields here]}. To meet these needs, cryptography is often employed to secure data. Cryptographic encryption schemes allow data to be transmitted over a insecure channel, and thus much research has been done on the development and application of various encryption schemes.

\textbf{[insert examples here]}. \textbf{[insert examples here]}.

However, recently, in addition to the secure transmission of data, there is also interest in the secure modification of data. \textbf{insert examples here}.

To allow for operations on encrypted data while maintaining data secrecy, homomorphic encryption schemes have been developed.

\textbf{[insert brief overview of homomorphic encryption schemes]}.
